Influence of Connectivity on Dung Beetle Communities

### 2025-04-24 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
formatting
removed sentence

Corridors are good and generally understood as beneficial for

@@

All dung beetles were counted and identified to species. 
 - We also dried and weighed individuals to estimate biomass 
 - what guides/keys did you do to ID? 
 - did you deposit vouchers and if so where are they available?

@@

### Overview
_Don't have to describe these, just do it and report in results. this is just to remind us of what to do_
1. how many beetles total
1. most common species overall. 
1. was. the same species the most common one in all habitats?
1. were there any that were caught in all habitats? Any restricted to only one?
1. any invasive / exotic species?
1. Table: count by species by habitat

>>>>

@@

All dung beetles were counted and identified to species.

 - We also dried and weighed individuals to estimate biomass  
 - what guides/keys did you do to ID?  
 - did you deposit vouchers and if so where are they available?

@@

_Don't have to describe these, just do it and report in results. this is just to remind us of what to do_

1. how many beetles total  
1. most common species overall.  
1. was. the same species the most common one in all habitats?  
1. were there any that were caught in all habitats? Any restricted to only one?  
1. any invasive / exotic species?  
1. Table: count by species by habitat.
